Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_appendix_training.tex
Appendix I: small changes.

While little training focuses specifically on sustainable
software, a variety of training activities increase researcher awareness 
and engagement with software engineering practices and software professionals.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.

>>>>

While little training focuses specifically on sustainable
software, a variety of training activities could increase researcher awareness of
and engagement with software professionals and software engineering practices.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.
